Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-11-10 grove-paper.tex
Finish figured and captions (Michael D. Adams)

\tikzset{
  every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{edge style/.style={
  draw,
  %color=gray,
  font={\small\ttfamily},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/graph style/.style={
  tree layout,
  level distance=0.5cm,
  level sep=0.5cm,
  sibling distance=0.5cm,
  sibling sep=0.1cm,
  part distance=0.1cm,
  part sep=0.1cm,
  component distance=0.1cm,
  component sep=0.1cm,
  nodes={
    draw,
    %color=gray,
    inner sep=2pt,
    rounded corners=1mm},
  edges={edge style},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{0}$}
}}
\tikzset{alice/.style={
  color=red!80!black,
  font={\bfseries\small},
  thick,
}}
\tikzset{bob/.style={
  color=green!60!black,
  font={\bfseries\small},
  thick,
}}
\tikzset{merge/.style={
  color=blue,
  font={\bfseries\small},
  thick,
}}
\tikzset{alice edge/.style={alice, edge style, font={\bfseries\small}}}
\tikzset{alice node/.style={alice}}
\tikzset{alice step/.style={alice}}
\tikzset{bob edge/.style={bob, edge style}, font={\bfseries\small}}
\tikzset{bob node/.style={bob}}
\tikzset{bob step/.style={bob}}
\tikzset{merge edge/.style={merge, edge style}, font={\bfseries\small}}
\tikzset{merge node/.style={merge}}
\tikzset{merge step/.style={merge,decorate,decoration={coil,amplitude=1.0pt,segment length=7.0pt,aspect=0}}}
\tikzset{star/.style={edge node={node[inner sep=0pt,at end,sloped] {\large\textbf{${}^{*}$}}}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureSimple
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\newcommand{\figureSimple}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-a}
TODO
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style, color=black] -> {
  "\vSimpleTimes" [> "\eSimpleTimes", >color=black, color=black] -> {
   "\vSimpleX" [> "\eSimpleX"', >color=black, color=black],
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole.
\autoref{fig:A simple tree with a hole-a}:~User interface.
\autoref{fig:A simple tree with a hole-b}:~Graph representation.}
\label{fig:A simple tree with a hole}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureConstructionAndDeletion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{ConstructionY}{R}%
\newvertex{ConstructionY}{y}%
\newcommand{\figureConstructionAndDeletion}{
\begin{figure}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-A simple tree with a hole-b-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:A simple tree with a hole-b}}}};
%%%%
\path (0cm,0cm) node (fig-Construction) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-A simple tree with a hole-b-x) to (-2em, 0cm |- fig-Construction);
\end{tikzpicture}
}
\label{fig:Construction and Deletion-a}
\label{fig:Construction}
\label{fig:Construction-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vConstructionY" [> "\eConstructionY", >alice edge, alice node]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Deletion) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Construction) to (-2em, 0cm |- fig-Deletion);
\end{tikzpicture}
}
\label{fig:Construction and Deletion-b}
\label{fig:Change-a}
\label{fig:Change}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   {},
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\path (-0.25cm,-1.7cm) graph[graph style] {
 "\vSimpleX"
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction and Deletion.}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureWrapping
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{WrapPlus}{Root}
\newvertex{WrapPlus}{+}
\newedge{WrapTimes}{L}
\newcommand{\figureWrapping}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Deletion) to (-2em, 0cm |- fig-Wrapping-a);
\end{tikzpicture}
}
\label{fig:Wrapping-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (0cm,-1.7cm) graph[graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-b) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Wrapping-a) to (-2em, 0cm |- fig-Wrapping-b);
\end{tikzpicture}
}
\label{fig:Wrapping-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus", >alice edge, alice node]
 }
};
\path (0cm,-1.7cm) graph[graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-c) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Wrapping-b) to (-2em, 0cm |- fig-Wrapping-c);
\end{tikzpicture}
}
\label{fig:Wrapping-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eWrapTimes"', >alice edge] -> {
    {},
    "\vConstructionY" [> "\eConstructionY"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping.  Note that this figure omits the orphaned \vSimpleX{} since it is no longer relevant to our narrative.}
\label{fig:Wrapping}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMovement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MoveTimes}{R}
\newcommand{\figureMovement}{
\begin{figure}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Wrapping-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Wrapping-c}}}};
%%%%
\path (0cm,0cm) node (fig-Moving-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Wrapping-c-x) to (-2em, 0cm |- fig-Moving-a);
\end{tikzpicture}
}
\label{fig:Move-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (0cm,-1.7cm) graph [graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Moving-b) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Moving-a) to (-2em, 0cm |- fig-Moving-b);
\end{tikzpicture}
}
\label{fig:Move-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes", >alice edge] -> {
    {},
    "\vConstructionY" [> "\eConstructionY"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \vSimpleTimes{} to the right child of~\vWrapPlus{}.}
\label{fig:Move}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureEditingDifferentParts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{DifferentAlice}{L}
\newvertex{DifferentAlice}{u}
\newedge{DifferentBob}{R}
\newvertex{DifferentBob}{v}
\newcommand{\figureEditingDifferentParts}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Moving-b) to (-2em, 0cm |- fig-Editing Different Parts of the Code-a);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"', >alice edge, alice node],
    "\vConstructionY" [> "\eConstructionY"]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-b) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Moving-b) to [out=15,in=165,star] (-2em, 0cm |- fig-Editing Different Parts of the Code-b);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    {},
    "\vDifferentBob" [> "\eDifferentBob", >bob edge, bob node]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-c) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Editing Different Parts of the Code-a) to [out=15,in=165] (-2em, 0cm |- fig-Editing Different Parts of the Code-c);
\path [draw,->,merge step] (fig-Editing Different Parts of the Code-b) to (-2em, 0cm |- fig-Editing Different Parts of the Code-c);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"', >merge edge, merge node],
    "\vDifferentBob" [> "\eDifferentBob", >merge edge, merge node]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code.}
\label{fig:Editing Different Parts of the Code}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureCommutativity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\figureCommutativity}{
\begin{figure}
\centering

TODO: commutativity diagram of screenshots with two cursors

TODO: include legend of arrow colors

TODO: move into section 2.3.1

TODO: star on multi-step arrows

\caption{TODO:Commutativity}
\label{fig:Commutativity}
\end{figure}
}

>>>>

\tikzset{
  %every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{edge style/.style={
  draw,
  %color=gray,
  font={\small\ttfamily},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/graph style/.style={
  tree layout,
  level distance=0.5cm,
  level sep=0.5cm,
  sibling distance=0.5cm,
  sibling sep=0.1cm,
  part distance=0.1cm,
  part sep=0.1cm,
  component distance=0.1cm,
  component sep=0.1cm,
  nodes={
    draw,
    %color=gray,
    inner sep=2pt,
    rounded corners=1mm},
  edges={edge style},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{0}$}
}}
\tikzset{alice/.style={
  color=red!80!black,
  font={\bfseries\small},
  thick,
}}
\tikzset{bob/.style={
  color=green!60!black,
  font={\bfseries\small},
  thick,
}}
\tikzset{merge/.style={
  color=blue,
  font={\bfseries\small},
  thick,
}}
\tikzset{alice edge/.style={alice, edge style, font={\bfseries\small}}}
\tikzset{alice node/.style={alice}}
\tikzset{alice step/.style={alice}}
\tikzset{bob edge/.style={bob, edge style}, font={\bfseries\small}}
\tikzset{bob node/.style={bob}}
\tikzset{bob step/.style={bob}}
\tikzset{merge edge/.style={merge, edge style}, font={\bfseries\small}}
\tikzset{merge node/.style={merge}}
\tikzset{merge step/.style={merge,decorate,decoration={coil,amplitude=1.0pt,segment length=7.0pt,aspect=0}}}
\tikzset{star/.style={edge node={node[inner sep=0pt,at end,sloped] {\large\textbf{${}^{*}$}}}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureSimple
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\newcommand{\figureSimple}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-a}
TODO
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style, color=black] -> {
  "\vSimpleTimes" [> "\eSimpleTimes", >color=black, color=black] -> {
   "\vSimpleX" [> "\eSimpleX"', >color=black, color=black],
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Code that Includes a Hole.
\autoref{fig:A simple tree with a hole-a}:~User Interface for the Code.
\autoref{fig:A simple tree with a hole-b}:~Graph Representation of the Code.}
\label{fig:A simple tree with a hole}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureConstructionAndDeletion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{ConstructionY}{R}%
\newvertex{ConstructionY}{y}%
\newcommand{\figureConstructionAndDeletion}{
\begin{figure}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-A simple tree with a hole-b-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:A simple tree with a hole-b}}}};
%%%%
\path (0cm,0cm) node (fig-Construction) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-A simple tree with a hole-b-x) to (-2em, 0cm |- fig-Construction);
\end{tikzpicture}
}
\label{fig:Construction and Deletion-a}
\label{fig:Construction}
\label{fig:Construction-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vConstructionY" [> "\eConstructionY", >alice edge, alice node]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Deletion) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Construction) to (-2em, 0cm |- fig-Deletion);
\end{tikzpicture}
}
\label{fig:Construction and Deletion-b}
\label{fig:Change-a}
\label{fig:Change}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   {},
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\path (-0.25cm,-1.7cm) graph[graph style] {
 "\vSimpleX"
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Construction and Deletion.}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureWrapping
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{WrapPlus}{Root}
\newvertex{WrapPlus}{+}
\newedge{WrapTimes}{L}
\newcommand{\figureWrapping}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Deletion) to (-2em, 0cm |- fig-Wrapping-a);
\end{tikzpicture}
}
\label{fig:Wrapping-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (0cm,-1.7cm) graph[graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-b) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Wrapping-a) to (-2em, 0cm |- fig-Wrapping-b);
\end{tikzpicture}
}
\label{fig:Wrapping-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus", >alice edge, alice node]
 }
};
\path (0cm,-1.7cm) graph[graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Wrapping-c) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Wrapping-b) to (-2em, 0cm |- fig-Wrapping-c);
\end{tikzpicture}
}
\label{fig:Wrapping-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eWrapTimes"', >alice edge] -> {
    {},
    "\vConstructionY" [> "\eConstructionY"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Wrapping.  (Note that this figure omits the orphaned \vSimpleX{} since it is no longer relevant to our narrative.)}
\label{fig:Wrapping}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMovement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MoveTimes}{R}
\newcommand{\figureMovement}{
\begin{figure}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Wrapping-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Wrapping-c}}}};
%%%%
\path (0cm,0cm) node (fig-Moving-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Wrapping-c-x) to (-2em, 0cm |- fig-Moving-a);
\end{tikzpicture}
}
\label{fig:Move-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (0cm,-1.7cm) graph [graph style] {
 "\vSimpleTimes" -> {
  {},
  "\vConstructionY" [> "\eConstructionY"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.43\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Moving-b) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Moving-a) to (-2em, 0cm |- fig-Moving-b);
\end{tikzpicture}
}
\label{fig:Move-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes", >alice edge] -> {
    {},
    "\vConstructionY" [> "\eConstructionY"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Repositioning Code.}
\label{fig:Move}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureEditingDifferentParts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{DifferentAlice}{L}
\newvertex{DifferentAlice}{u}
\newedge{DifferentBob}{R}
\newvertex{DifferentBob}{v}
\newcommand{\figureEditingDifferentParts}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Moving-b) to (-2em, 0cm |- fig-Editing Different Parts of the Code-a);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"', >alice edge, alice node],
    "\vConstructionY" [> "\eConstructionY"]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-b) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Moving-b) to [out=15,in=165,star] (-2em, 0cm |- fig-Editing Different Parts of the Code-b);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    {},
    "\vDifferentBob" [> "\eDifferentBob", >bob edge, bob node]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Different Parts of the Code-c) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Editing Different Parts of the Code-a) to [out=15,in=165] (-2em, 0cm |- fig-Editing Different Parts of the Code-c);
\path [draw,->,merge step] (fig-Editing Different Parts of the Code-b) to (-2em, 0cm |- fig-Editing Different Parts of the Code-c);
\end{tikzpicture}
}
\label{fig:Editing Different Parts of the Code-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
  {},
  "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"', >merge edge, merge node],
    "\vDifferentBob" [> "\eDifferentBob", >merge edge, merge node]
  }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Users Editing Different Parts of the Code.}
\label{fig:Editing Different Parts of the Code}
\end{figure}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureCommutativity
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newcommand{\figureCommutativity}{
% \begin{figure}
% \centering
% \begin{figure}
% \centering
% \begin{tikzpicture}
% \path (-3cm, 0cm) node (a) [align=center]       {Original \\ Version};
% \path ( 0cm, 1cm) node (b) [align=center,alice node] {Alice's  \\ Version};
% \path ( 0cm,-1cm) node (c) [align=center,bob node]   {Bob's    \\ Version};
% \path ( 3cm, 0cm) node (d) [align=center]       {Combined \\ Version};
% \path [draw,->,alice step] (a) -- node [pos=0.7,auto] {Alice's Edits} (b);
% \path [draw,->,bob step]   (a) -- node [pos=0.7,auto,swap]      {Bob's Edits}   (c);
% \path [draw,->,merge step] (b) -- node [pos=0.3,auto] {Sync} (d);
% \path [draw,->,merge step] (c) -- node [pos=0.3,auto,swap]      {Sync} (d);
% \end{tikzpicture}
% \caption{TODO:Commutativity}
% \label{fig:Commutativity}
% \end{figure}
% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureEditingNestedParts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{NestedAlice}{L}
\newvertex{NestedAlice}{w}
\newedge{NestedBob}{L}
\newcommand{\figureEditingNestedParts}{
\begin{figure}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Editing Different Parts of the Code-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Editing Different Parts of the Code-c}}}};
%%%%
\path (0cm,0cm) node (fig-Editing Nested Parts of the Code-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Editing Different Parts of the Code-c-x) to[star] (-2em, 0cm |- fig-Editing Nested Parts of the Code-a);
\end{tikzpicture}
}
\label{fig:Editing Nested Parts of the Code-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vNestedAlice" [> "\eNestedAlice"', >alice edge, alice node],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Nested Parts of the Code-b) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Editing Different Parts of the Code-c-x) to [out=15,in=165,star] (-2em, 0cm |- fig-Editing Nested Parts of the Code-b);
\end{tikzpicture}
}
\label{fig:Editing Nested Parts of the Code-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"', >bob edge] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.25\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Editing Nested Parts of the Code-c) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Editing Nested Parts of the Code-a) to [out=15,in=165] (-2em, 0cm |- fig-Editing Nested Parts of the Code-c);
\path [draw,->,merge step] (fig-Editing Nested Parts of the Code-b) to [out=15,in=165] (-2em, 0cm |- fig-Editing Nested Parts of the Code-c);
\end{tikzpicture}
}
\label{fig:Editing Nested Parts of the Code-c}
\label{fig:Editing Nested-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"', >merge edge] -> {
    "\vNestedAlice" [> "\eNestedAlice"', >merge edge, merge node],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Users Editing Nested Parts of the Code.}
\label{fig:Editing Nested Parts of the Code}
\end{figure}
}
